---
title: "Chapter 6: Long Term Pathways"
output: 
  html_document:
    toc: true
    toc_float: true
date: "`r Sys.time()`"
params:
  mode: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = here::here())
```

```{r}
if(is.null(params$mode)) {
  source("packages.R")
  devtools::load_all()
}

# load data from targets pipeline
targets::tar_load(config)
targets::tar_load(clean_data)
targets::tar_load(figmap_leep_timeseries)
targets::tar_load(figmap_leep_cone)
targets::tar_load(figmap_leep_stackbar)
targets::tar_load(data_min)
targets::tar_load(data_raw)

# palettes
subpalettes = create_subpalettes(figmap_leep_timeseries, config)
```

## 6.1/ES3 comparing us climate targets with scenario modeling through 2050

```{r}
fig_no = 6.1

ghgi <- clean_data %>%
  filter(model == "EPA-GHGI" & 
           variable == "Emissions|GHG|Net" &
           year >= 2005) %>%
  mutate(value = value/1000)

connect <- ghgi[ghgi$year == 2021,] %>%
  select(year, value)%>%
  mutate(ymin = value, 
         ymax = value, 
         med = value) %>%
  select(-value)

lts <- clean_data %>%
  filter(model == "GCAM-LTS" &
           variable %in% c(
             "Emissions|CO2",
             "Emissions|CH4",
             "Emissions|N2O",
             "Emissions|F-Gases",
             "Carbon Sequestration|CCS|Biomass|Energy",
             "Carbon Sequestration|LULUCF",
             "Carbon Sequestration|Direct Air Capture|Net")) %>%
  mutate(value = value/1000) %>%
  mutate(value = case_when(
    grepl("Sequestration", variable) ~ value * -1, 
    T ~ value
  )) %>%
  group_by(year, scenario) %>%
  summarize(value = sum(value)) %>%
  ungroup() %>%
  group_by(year) %>%
  summarize(ymax = max(value), 
            ymin = min(value), 
            med = median(value)) %>%
  filter(year >= 2021) %>%
  filter(year <= 2035)

target_30 = lts %>% filter(year == 2030)
target_35 = lts %>% filter(year == 2035)

lts <- rbind(lts, connect)

IRA <- clean_data %>%
  filter(scenario %in% c("IRA","No IRA") &
           year %in% c(2025, 2030, 2035) &
           variable %in% c("Emissions|CO2",
                           "Emissions|Non-CO2 GHG",
                           "Carbon Sequestration|CCS|Biomass|Energy",
                           "Carbon Sequestration|LULUCF",
                           "Carbon Sequestration|Direct Air Capture|Net")) %>%
  # MARKAL non-co2 too low, regen doesnt report non-energy co2, nems-op doesnt report non-energy co2
  filter(!model %in% c("NEMS-EIA","MARKAL-NETL")) %>% #"REGEN-EPRI", "NEMS-OP", 
  group_by(year, model, scenario) %>%
  summarise(value = sum(value)/1000)
  
histcon <- IRA %>%
  group_by(model, scenario) %>%
  slice(1) %>%
  mutate(
    year = 2021,
    value = ghgi$value[ghgi$year == 2021])

IRA <- rbind(IRA, histcon)

IRA <- IRA %>%
  mutate(alpha = case_when(
    model == "USREP-ReEDS" ~ 1, 
    model == "GCAM-PNNL" ~ 1, 
    model == "IPM-EPA" ~ 1,
    scenario == "Historic" ~ 1,
    T ~ 0.8
  )) 

yscale = scale_y_continuous(limits = c(0,8), expand = c(0,0))

fin = ggplot() + 
  geom_line(ghgi, mapping = aes(x = year, y = value, color = "Historic"), size = 0.8) +
  geom_line(lts, mapping = aes(x=year, y = ymin, color = "LTS"), linetype = "dashed", size = 0.8, color = "#767684")+
  geom_line(lts, mapping = aes(x=year, y = ymax, color = "LTS"), linetype = "dashed", size = 0.8, color = "#767684")+
  geom_ribbon(lts, mapping = aes(x=year, ymax = ymax, ymin = ymin, fill = "LTS"), alpha = 0.2) + 
  geom_line(IRA, mapping = aes(x=year, y = value, group = interaction(model, scenario), color = scenario, alpha = alpha)) + 
  scale_color_manual(name = "", 
                     breaks = c("IRA", "No IRA", "Historic", "LTS"), 
                     values = c("#0388B3","#F28063", "black", "#767684"), 
                     labels = c("IRA", "No IRA", "Historic Emissions", "Emissions Targets")) + 
  scale_fill_manual(name = "", 
                    breaks = c("IRA", "No IRA", "Historic", "LTS"), 
                     values = c("#0388B3","#F28063", "black", "#767684"), 
                     labels = c("IRA", "No IRA", "Historic Emissions", "Emissions Targets")) +
  theme_emf() + 
  labs(title = "", 
       y = expression(paste("Net GHG Emissions (MMt ", CO[2], "e)", sep = "")), 
       x = "") +
  scale_alpha(range = c(0.6, 1), guide = F) + 
  yscale + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.ticks = element_blank(),
        legend.box = "vertical",
        legend.text = element_text(size = 8),
        legend.spacing.y = unit(0.5, "mm"),
        legend.position = c(0.2, 0.3), 
        legend.background = element_blank()) + 
  scale_x_continuous(breaks = c(2005, 2021, 2025, 2030, 2035)) + 
  guides(fill = guide_legend(nrow=4, byrow = T)) +
  geom_hline(aes(yintercept=0)) +
  theme(plot.margin = margin(0, 0, 0, 0))
fin

base <- clean_data %>%
  filter(variable == "Emissions|GHG|Net" & year == 2005 & model == "EPA-GHGI")

baseline = base$value[1]/1000

df_30 = IRA %>%
  filter(year %in% c(2030))
df_stat_30 = df_30 %>%
  group_by(scenario, year) %>%
  summarise(mean = mean(value),
            median = median(value)) %>%
  rbind(data.frame(scenario="Historic",year=2030,mean=baseline,median=baseline)) %>%
  rbind(data.frame(scenario="zero",year=2030,mean=0,median=0))

df_35 = IRA %>%
  filter(year %in% c(2035))
df_stat_35 = df_35 %>%
  group_by(scenario, year) %>%
  summarise(mean = mean(value),
            median = median(value)) %>%
  rbind(data.frame(scenario="Historic",year=2035,mean=baseline,median=baseline)) %>%
  rbind(data.frame(scenario="zero",year=2035,mean=0,median=0))
  
dots_30 = ggplot() +
  geom_point(
    data = df_30,
    aes(x = year,y = value,alpha = alpha,color = scenario),
    shape = 1,size = 1.5,position = position_dodge(width = 0.1)) +
  geom_segment(
    data = df_stat_30,
    aes(x = year - 0.025,
        xend = year + 0.025,
        y = median,
        yend = median,
        color = scenario)) +
  geom_rect(
    data = target_30,
    aes(ymin = ymin, 
        ymax = ymax,
        xmin = year - 0.025,
        xmax = year + 0.025),
    alpha = 0.2
  ) +
  scale_x_continuous(
    breaks = c(2030),
    labels = c("2030"),
    limits = c(2029.9, 2030.1)) +
  yscale +
  theme_emf() +
  scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
  scale_alpha(range = c(0.4, 1), guide = F) +
  theme(
    panel.grid = element_blank(),
    plot.title = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_blank(),
    legend.position = "none",
    plot.margin = margin(0, 0, 0, 0))
  
# dot plot for 2035
dots_35 = ggplot() +
  geom_point(
    data = df_35,
    aes(
      x = year,
      y = value,
      color = scenario,
      alpha = alpha
    ),
    shape = 1,
    size = 1.5,
    position = position_dodge(width = 0.1)
  ) +
  geom_segment(data = df_stat_35,
               aes(
                 x = year - 0.025,
                 xend = year + 0.025,
                 y = median,
                 yend = median,
                 color = scenario
               )) +
  geom_rect(
    data = target_35,
    aes(ymin = ymin, 
        ymax = ymax,
        xmin = year - 0.025,
        xmax = year + 0.025),
    alpha = 0.2
  ) +
  scale_x_continuous(
    breaks = c(2035),
    labels = c("2035"),
    limits = c(2034.9, 2035.1)
  ) +
  yscale +
  theme_emf() +
  scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
  scale_alpha(range = c(0.4, 1), guide = F) +
  theme(
    panel.grid = element_blank(),
    plot.title = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_blank(),
    legend.position = "none",
    plot.margin = margin(0, 0, 0, 0)
  ) 

final = fin + dots_30 + dots_35 +
    plot_layout(widths = c(10,1,1)) +
    theme(plot.margin = margin(0,0,0,0))
final

savefig(final, fig_no)
```

### Morgan's Stats

```{r}
table1 = IRA %>%
  ungroup() %>%
  select(-alpha) %>%
  filter(year %in% c(2025, 2030, 2035)) %>%
  mutate(
    diff_2005 = baseline - value,
    per_diff = diff_2005/baseline * 100) %>%
  mutate_if(is.numeric, round, 2)

write.csv(table1, "output/final_figures/data/6.1_allstats.csv", row.names = FALSE)

table2 = table1 %>%
  group_by(year,scenario) %>%
  summarise(
    min_ab = min(value),
    max_ab = max(value),
    median_ab = median(value),
    min_diff = min(per_diff),
    max_diff = max(per_diff),
    median_diff = median(per_diff)
            ) %>%
  mutate_if(is.numeric, round, 2)

write.csv(table2, "output/final_figures/data/6.1_smallstats.csv", row.names = FALSE)
```

### Table 6.1

```{r}
title = "GHG Emissions Exec"

base <- clean_data %>%
  filter(variable == "Emissions|GHG|Net" & year == 2005 & model == "EPA-GHGI")

baseline = base$value[1]

base <- as.data.frame(base) %>%
  select(Year = year, 
         `Absolute Level (Mt CO2)` = value) %>%
  mutate(Scenario = "Baseline", 
    `% Reductions from 2005` = NA,
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (Mt CO2)` = NA)  %>%
  select(Year, Scenario, `Absolute Level (Mt CO2)`, `% Reductions from 2005`, `% Reductions from No IRA`, `Reductions from No IRA (Mt CO2)`)

NoIRA <- IRA %>%
  filter(scenario == "No IRA" &
           year %in% c(2025,2030,2035)) %>%
  group_by(year) %>%
  summarize(`No IRA Median` = median(value), 
            `No IRA Min` = min(value),
            `No IRA Max` =  max(value))%>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (Mt CO2)") %>%
  mutate(`2005_perc_red` = ((baseline-`Absolute Level (Mt CO2)`)/baseline) * 100) %>%
  mutate(
    Year = year, 
    `% Reductions from 2005` = `2005_perc_red`, 
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (Mt CO2)` = NA
  ) %>%
  select(!year & !`2005_perc_red`)

IRA <- IRA %>%
  filter(scenario == "IRA" &
           year %in% c(2025,2030,2035)) %>%
  select(!scenario) %>%
  group_by(year) %>%
  summarize(
    `IRA Max` = max(value), 
    `IRA Min` = min(value), 
    `IRA Median` = median(value)) %>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (Mt CO2)") %>%
  mutate(
    `% Reductions from 2005` = ((baseline-`Absolute Level (Mt CO2)`)/baseline) * 100
  )%>%
  mutate(
    `% Reductions from No IRA` = case_when(
      year == 2025 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2025 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (Mt CO2)`)/NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2025 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2025 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2025 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (Mt CO2)`)/NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2025 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2025 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2025 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (Mt CO2)`)/NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2025 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
            year == 2035 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (Mt CO2)`)/NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (Mt CO2)`)/NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (Mt CO2)`)/NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]) * 100
    ), 

    `Reductions from No IRA (Mt CO2)` = case_when(
      year == 2025 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2025 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (Mt CO2)`), 
      
      year == 2025 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2025 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (Mt CO2)`), 
      
      year == 2025 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2025 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (Mt CO2)`),
      
            year == 2035 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (Mt CO2)`), 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (Mt CO2)`), 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (Mt CO2)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (Mt CO2)`)
    )
  ) %>%
  rename(Year = year)

IRA = rbind(NoIRA, IRA)

IRA$`Absolute Level (Mt CO2)` = round(IRA$`Absolute Level (Mt CO2)`, 3)
IRA$`% Reductions from 2005` = round(IRA$`% Reductions from 2005`, 3)
IRA$`% Reductions from No IRA` = round(IRA$`% Reductions from No IRA`, 3)
IRA$`Reductions from No IRA (Mt CO2)` = round(IRA$`Reductions from No IRA (Mt CO2)`,3)

IRA <- IRA %>%
  arrange(desc(IRA)) %>%
  arrange(Year)

IRA = rbind(base, IRA)

IRA %>%
tableHTML(caption = paste(title), rownames = F)
```

## 6.2 us energy emissions by sector comparing ira modeling to lts pathways

```{r}
# LTS Cone plot for economy-wide emissions

# buildings cone
mid = lts_coneplot_with_dots(config, clean_data, figmap_leep_cone, 23, 24, "United States", -100, 2500, "Buildings", 8, "median", facet = TRUE) +
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
mid

# transportation cone
left = lts_coneplot_with_dots(config, clean_data, figmap_leep_cone, 21, 22, "United States", -100, 2500, "Transportation", 8, "median", facet = TRUE)
left

# industry cone
right = lts_coneplot_with_dots(config, clean_data, figmap_leep_cone, 25, 26, "United States", -100, 2500, "Industrial", 8, "median", facet = TRUE) +
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
right

# electric sector cone
top = lts_coneplot_with_dots(config, clean_data, figmap_leep_cone, 19, 20, "United States", -100, 2500, "Electric Sector CO2 Emissions", 12, "median", facet = FALSE)
top

# put 'em all together
bottom = (left | mid | right) + plot_annotation(title = "Direct and Indirect CO2 Emissions", theme = theme(plot.title = element_text(hjust = 0.5, size = 12), plot.margin = margin(0,0,0,0)))
bottom

combined = (wrap_elements(top) / wrap_elements(bottom))
combined

ggsave(filename = "output/final_figures/svg/Fig6.2_LTS_cone_indirect_emissions_TOTAL.svg", 
       combined, width = 7, height = 5, units = "in")
ggsave(filename = "output/final_figures/png/Fig6.2_LTS_cone_indirect_emissions_TOTAL.png", 
       combined, width = 7, height = 5, units = "in")

# supporting data
dta = data.frame()
for (i in c(seq(19,26,by = 1))) {
  dta = rbind(dta, data_from_graph("cone_uncertainty", config, clean_data, figmap_leep_cone, i, "United States"))
}
dta %>% write.csv("output/final_figures/data/Fig6.2_LTS_cone_indirect_emissions_TOTAL.csv", row.names = FALSE)

```

## 6.3 energy used in the transportation sector, by fuel type, comparing ira scenarios to lts pathways

```{r}
p3 = lts_coneplot_with_dots(config, clean_data, figmap_leep_cone, 11, 12, "United States", 0, 30, title = "Transportation Sector Final Energy" , "median", facet = TRUE) +
  facet_grid(~factor(variable_rename, levels=c('Fossil', 'Electricity', 'Alternative Fuels'))) +
  theme(plot.title = element_blank())
p3
ggsave(filename = "output/final_figures/svg/Fig6.3_LTS_cone_transport_facet.svg",p3, width = 7, height = 5, units = "in")
ggsave(filename = "output/final_figures/png/Fig6.3_LTS_cone_transport_facet.png",p3, width = 7, height = 5, units = "in")

dta1 = data_from_graph("cone_uncertainty", config, clean_data, figmap_leep_cone, 11, "United States")
dta2 = data_from_graph("cone_uncertainty", config, clean_data, figmap_leep_cone, 12, "United States")
dta = rbind(dta1, dta2)
dta %>% write.csv("output/final_figures/data/Fig6.3_LTS_cone_transport_facet.csv", row.names = FALSE)
```

## 6.4 energy used in the buildings sector, by fuel type, comparing ira scenarios to lts pathways

```{r}
p = lts_coneplot_with_dots(config, clean_data, figmap_leep_cone, 15, 16, "United States", 0, 15, title = "Buildings Sector Final Energy", "median", facet = TRUE) +
  facet_grid(~factor(variable_rename, levels=c('Electricity', 'Non-Electric'))) +
  theme(plot.title = element_blank())
p
ggsave(filename = "output/final_figures/svg/Fig6.4_LTS_cone_buildings_facet.svg",p, width = 7, height = 5, units = "in")
ggsave(filename = "output/final_figures/png/Fig6.4_LTS_cone_buildings_facet.png",p, width = 7, height = 5, units = "in")

dta1 = data_from_graph("cone_uncertainty", config, clean_data, figmap_leep_cone, 13, "United States")
dta2 = data_from_graph("cone_uncertainty", config, clean_data, figmap_leep_cone, 14, "United States")
dta = rbind(dta1, dta2)
dta %>% write.csv("output/final_figures/data/Fig6.4_LTS_cone_industry_facet.csv", row.names = FALSE)
```

## 6.5 energy used in the industrial sector, by fuel type, comparing ira scenarios to lts pathways

```{r}
p4 = lts_coneplot_with_dots(config, clean_data, figmap_leep_cone, 13, 14, "United States", 0, 23, title = "Industrial Sector Final Energy", "median", facet = TRUE) +
  facet_grid(~factor(variable_rename, levels=c('Fossil', 'Electricity', 'Alternative Fuels'))) +
  theme(plot.title = element_blank())
p4
ggsave(filename = "output/final_figures/svg/Fig6.5_LTS_cone_industry_facet.svg", p4, width = 7, height = 5, units = "in")
ggsave(filename = "output/final_figures/png/Fig6.5_LTS_cone_industry_facet.png", p4, width = 7, height = 5, units = "in")

dta1 = data_from_graph("cone_uncertainty", config, clean_data, figmap_leep_cone, 13, "United States")
dta2 = data_from_graph("cone_uncertainty", config, clean_data, figmap_leep_cone, 14, "United States")
dta = rbind(dta1, dta2)
dta %>% write.csv("output/final_figures/data/Fig6.5_LTS_cone_industry_facet.csv", row.names = FALSE)
```

## GHG emissions

```{r}
fig_no = "K.1"

models_exclude = c("GHGI-LTS")

non_co2 = read.csv("./data-extra/ghg/non_co2.csv")

ghg = clean_data %>% 
  filter(variable %in% c(
    "Emissions|CO2",
    "Emissions|N2O",
    "Emissions|CH4",
    "Emissions|F-Gases"
  ), scenario %in% c("IRA", "No IRA","Historic"), 
  !(model %in% models_exclude),
  ((year >= 2005 & year <= 2021) | year %in% c("2025", "2030", "2035")))

historic = ghg %>% filter(scenario == "Historic")
ghg = ghg %>% filter(year > 2021)

all_combos = ghg %>% expand(model, scenario, year, variable)

dta = ghg %>% 
  right_join(all_combos) %>%
  full_join(non_co2, by = c("variable", "year")) %>%
  mutate(value = case_when(model == "GCAM-PNNL" ~ value, 
                    !is.na(replace) ~ replace, 
                    TRUE ~ value)) %>%
  select(-replace)

more_combos = ghg %>% expand(model, scenario, year)
land_sink = data.frame("variable" = c("Emissions|LULUCF","Emissions|LULUCF","Emissions|LULUCF"), "year" = c(2025, 2030, 2035), "value" = c(-672,-604,-602)) %>%
  right_join(more_combos)

dta = bind_rows(dta, land_sink)

dta %>% write.csv("GHG_estimates.csv", row.names = F)

dta = bind_rows(dta, historic) %>%
  group_by(model, scenario, year) %>%
  summarize(value = sum(value)) %>%
  mutate(alpha = 1)
  
dta_fill = dta %>% filter(year == 2025) %>%
  mutate(year = 2021, 
         value = 6418.04)

dta = bind_rows(dta, dta_fill) %>% mutate(variable_rename = "GHGs")

ghg = spg2(df = dta, title = "", yname = expression(paste("GHG Emissions (Mt C", O[2], "e/yr)")), gd = "none", ymin = 0, ymax = 8000, 
              ybreaks = waiver(), yax_format = scales::comma, annotate = 1, 
              historic_coord = c(2015,7500), preira_coord = c(2030, 5500), ira_coord = c(2027, 4100),
              config = config, figmap_leep_timeseries = figmap_leep_timeseries)

ghg_dots = dotted(ghg$data, ghg$figure, "median", 0, 8000, config, figmap_leep_timeseries)
ghg_dots
saveall(ghg_dots, dta, fig_no)
```

