---
title: "Chapter 2: Electricity"
output: 
  html_document:
    toc: true
    toc_float: true
date: "`r Sys.time()`"
params:
  mode: NULL
  format: "svg"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = here::here())
```

```{r}
if(is.null(params$mode)) {
  source("packages.R")
  devtools::load_all()
}

# load data from targets pipeline
targets::tar_load(config)
targets::tar_load(clean_data)
targets::tar_load(figmap_leep_timeseries)
targets::tar_load(figmap_leep_cone)
targets::tar_load(figmap_leep_stackbar)
targets::tar_load(data_min)
targets::tar_load(data_raw)

# create workbook for saving figure data
# data_wb <- createWorkbook()

# format toggle
format <- params$format

# palettes
subpalettes = create_subpalettes(figmap_leep_timeseries, config)
```

## 2.1 co2 emissions from the power sector in the us, compared to economy-wide co2 emissions

```{r}
data <- clean_data %>%
  filter(model == "EPA-GHGI") %>%
  filter(year >= 2005) %>%
  filter(variable == "Emissions|CO2|Energy|Demand|Buildings|Commercial|Coal"|
         variable == "Emissions|CO2|Energy|Demand|Buildings|Commercial|Gas" |
         variable == "Emissions|CO2|Energy|Demand|Buildings|Commercial|Oil" |
         variable == "Emissions|CO2|Energy|Demand|Buildings|Residential|Coal" |
         variable == "Emissions|CO2|Energy|Demand|Buildings|Residential|Gas" |
         variable == "Emissions|CO2|Energy|Demand|Buildings|Residential|Oil" |
         variable == "Emissions|CO2|Energy|Demand|Industry|Coal" |
         variable == "Emissions|CO2|Energy|Demand|Industry|Gas" |
         variable == "Emissions|CO2|Energy|Demand|Industry|Oil" |
         variable == "Emissions|CO2|Energy|Demand|Transportation|Gas" |
         variable == "Emissions|CO2|Energy|Demand|Transportation|Oil" |
         variable == "Emissions|CO2|Energy|Supply|Electricity|Coal" |
         variable == "Emissions|CO2|Energy|Supply|Electricity|Gas" |
         variable == "Emissions|CO2|Energy|Supply|Electricity|Oil") %>%
  mutate(variable_rename = case_when(
    grepl("Demand", variable) ~ "Other Sectors",
    grepl("Coal", variable) ~ "Coal", 
    grepl("Gas", variable) ~ "Gas", 
    grepl("Oil", variable) ~ "Petroleum",
  )) %>%
  group_by(year, variable_rename) %>%
  summarise(value = sum(value)) %>%
  mutate(alpha = case_when(
    variable_rename == "Other Sectors" ~ 0.5, 
    T ~ 1))

data$variable_rename <- factor(data$variable_rename, level = c("Other Sectors", "Coal", "Gas", "Petroleum"))

fig = ggplot(data, aes(fill = variable_rename, y = value, alpha = alpha, x = year, color = variable_rename)) + 
  geom_bar(position = "stack", stat = "identity") + 
  theme_emf() +
  labs(title = "",
         x = "",
         y = expression(paste("Mt C", O[2], "/yr"))) +
    scale_y_continuous(limits = c(0, 6000), labels = scales::comma) +
    scale_x_continuous(breaks = c(2005, 2021)) + 
    theme(panel.spacing.x = unit(4, "mm"), legend.position = "bottom") +
    scale_alpha(range = c(0.6, 1), guide = F)+
  scale_color_manual(breaks = c( "Coal", "Gas", "Petroleum", "Other Sectors"), 
                     values = c( "#003052", "#BC8F73", "#733D3D", "#DEDEDE")) +
  scale_fill_manual(breaks = c( "Coal", "Gas", "Petroleum", "Other Sectors"), 
                     values = c( "#003052", "#BC8F73", "#733D3D", "#DEDEDE")) 

print(fig)
```

## 2.2 us electricity generation and capacity shares by fuel type, 2021

```{r}
clean_data10 = clean_data %>% 
  filter(datasrc == 'EIA-IEA-bistline_historic.csv')

fig = print_graph("stacked_bar", config, clean_data10, figmap_leep_stackbar, 14, "United States", 
                  level_var = c("Other", "Renewables", "Nuclear", "Oil", "Natural Gas", "Coal")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5), plot.title = element_blank()) +
  bottom1

fig
#dta = data_from_graph("stacked_bar", config, clean_data, figmap_leep_stackbar, 3, "United States")

ggsave(filename = "output/final_figures/svg/Fig2.2_hist_generation_mix.svg",fig, width = 7, height = 5, units = "in")
ggsave(filename = "output/final_figures/png/Fig2.2_hist_generation_mix.png",fig, width = 7, height = 5, units = "in")

# supporting data
dta = data_from_graph("stacked_bar", config, clean_data10, figmap_leep_stackbar, 14, "United States")
dta %>% write.csv("output/final_figures/data/Fig2.2_hist_generation_mix.csv", row.names = FALSE)
```

## 2.3 us power sector co2 emissions

```{r}
ElecSpg = spg(
  98,
  "EPA-GHGI",
  "",
  expression(paste("Mt C", O[2], "/yr")),
  gd = "none",
  c("Scout-LEEP"),
  0,
  2500,
  c(0, 500, 1000, 1500, 2000, 2500),
  scales::comma) +
  annotate("text", x = 2015, y = 2250, label = "Historic", color = "black") + 
  annotate("text", x = 2027.5, y = 1750, label = "No IRA", color = "#F28063") + 
  annotate("text", x = 2023, y = 650, label = "IRA", color = "#0388B3")

ElecDot = dotted(ElecSpg$data, ElecSpg, "median", 0, 2500)

ElecTab = html(ElecSpg$data, "Electricity CO<sub>2<sub>")

print(ElecDot)
ElecTab
```

## 2.4 us power sector generation from high and low/zero emitting generation

```{r}
##### Data #####
fig = print_graph("time_series", config, clean_data, figmap_leep_timeseries, 16, "United States")

fig$data <- fig$data %>%
  filter(year == 2021 | year == 2030 | year == 2035)%>%
  filter(!model == "EIA") %>%
  filter(!model == "EIA-STEO") %>%
  mutate(value = value/0.0036, 
         unit = "TWh")

ymin = 0
ymax = 2600
metric = "median"

total <- fig$data %>%
  group_by(scenario, model, year) %>%
  summarise(value = sum(value)) %>%
  mutate(variable_rename = "Total")%>%
  mutate(alpha = case_when(
    model == "USREP-ReEDS" ~ 1, 
    model == "GCAM-PNNL" ~ 1, 
    model == "IPM-EPA" ~ 1,
    scenario == "Historic" ~ 1,
    T ~ 0.8
  ))

low <- fig$data %>%
  filter(variable_rename == "CCS" | 
         variable_rename == "Other" |
         variable_rename == "Nuclear" |
         variable_rename == "Solar" |
         variable_rename == "Wind"
) %>%
  group_by(scenario, model, year) %>%
  summarise(value = sum(value)) %>%
  mutate(variable_rename = "Total_Low")%>%
  mutate(alpha = case_when(
    model == "USREP-ReEDS" ~ 1, 
    model == "GCAM-PNNL" ~ 1, 
    model == "IPM-EPA" ~ 1,
    scenario == "Historic" ~ 1,
    T ~ 0.8
  ))

high <- fig$data %>%
  filter(variable_rename == "Coal" |
         variable_rename == "Natural Gas" |
         variable_rename == "Oil"
) %>%
  group_by(scenario, model, year) %>%
  summarise(value = sum(value)) %>%
  mutate(variable_rename = "Total_High")%>%
  mutate(alpha = case_when(
    model == "USREP-ReEDS" ~ 1, 
    model == "GCAM-PNNL" ~ 1, 
    model == "IPM-EPA" ~ 1,
    scenario == "Historic" ~ 1,
    T ~ 0.8
  ))

individual <- fig$data %>%
  mutate(
    variable_rename = case_when(variable_rename == "Oil" ~ "Other", 
                                T ~ variable_rename)
  ) %>%
  group_by(year, variable_rename, model, scenario) %>%
  summarise(value = sum(value))%>%
  mutate(alpha = case_when(
    model == "USREP-ReEDS" ~ 1, 
    model == "GCAM-PNNL" ~ 1, 
    model == "IPM-EPA" ~ 1,
    scenario == "Historic" ~ 1,
    T ~ 0.8
  ))




##### All Total #####
df_21 = total %>%
  filter(year %in% c(2021))
df_stat_21 = df_21 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_30 = total %>%
  filter(year %in% c(2030))
df_stat_30 = df_30 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_35 = total %>%
  filter(year %in% c(2035))
df_stat_35 = df_35 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

mean_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","mean"]$mean - df_stat_30[df_stat_30$scenario == "IRA","mean"]$mean
mean_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","mean"]$mean - df_stat_35[df_stat_35$scenario == "IRA","mean"]$mean

median_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","median"]$median - df_stat_30[df_stat_30$scenario == "IRA","median"]$median
median_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","median"]$median - df_stat_35[df_stat_35$scenario == "IRA","median"]$median

stats = data.frame("year" = c(2030, 2035, 2030, 2035), "metric" = c("mean","mean","median","median"), 
                   "difference" = c(mean_diff_30, mean_diff_35,median_diff_30, median_diff_35))

data = rbind(df_21, df_30, df_35) 

 

data_total <- data %>%
  mutate(axe = case_when(
    year == 2021 ~ 1, 
    year == 2030 ~ 2, 
    year == 2035 ~ 3
  )) %>%
  mutate(scenario = case_when(
    year == 2021 ~ "Historic", 
    T ~ scenario)
  )

dots_Total = ggplot(data = data_total, aes(x = axe, y = value,  color = scenario)) +
  geom_point(aes(alpha = alpha), shape = 1, size = 1.5, position = position_dodge(width = -0.5)) +
  geom_segment(data = df_stat_35, aes(x = 2.94, xend = 3.06, y = median, yend = median, color = scenario), size = 0.5) +
  geom_segment(data = df_stat_30, aes(x = 1.94, xend = 2.06, y = median, yend = median, color = scenario), size = 0.5) +
    facet_wrap(~"Total Generation") +
    scale_y_continuous(limits = c(ymin, 6500), breaks = c(0, 3250 , 6500), labels = scales::comma) +
    scale_x_continuous(breaks = c(1,2,3), labels = c("2021", "2030", "2035")) +
    theme_emf() +
    labs(y = "TWh") +
    scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.x = element_blank(),
          axis.ticks = element_blank(),
          legend.position = "none", 
          plot.margin = margin(0,0,0,0)) + 
  scale_alpha(range = c(0.6, 1), guide = F)

##### Low Total #####
df_21 = low %>%
  filter(year %in% c(2021))
df_stat_21 = df_21 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_30 = low %>%
  filter(year %in% c(2030))
df_stat_30 = df_30 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_35 = low %>%
  filter(year %in% c(2035))
df_stat_35 = df_35 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

mean_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","mean"]$mean - df_stat_30[df_stat_30$scenario == "IRA","mean"]$mean
mean_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","mean"]$mean - df_stat_35[df_stat_35$scenario == "IRA","mean"]$mean

median_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","median"]$median - df_stat_30[df_stat_30$scenario == "IRA","median"]$median
median_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","median"]$median - df_stat_35[df_stat_35$scenario == "IRA","median"]$median

stats = data.frame("year" = c(2030, 2035, 2030, 2035), "metric" = c("mean","mean","median","median"), 
                   "difference" = c(mean_diff_30, mean_diff_35,median_diff_30, median_diff_35))

data = rbind(df_21, df_30, df_35) 

 

data_Low <- data %>%
  mutate(axe = case_when(
    year == 2021 ~ 1, 
    year == 2030 ~ 2, 
    year == 2035 ~ 3
  )) %>%
  mutate(scenario = case_when(
    year == 2021 ~ "Historic", 
    T ~ scenario)
  )

dots_Low = ggplot(data = data_Low, aes(x = axe, y = value,  color = scenario)) +
  geom_point(aes(alpha = alpha), shape = 1, size = 1.5, position = position_dodge(width = -0.5)) +
  geom_segment(data = df_stat_35, aes(x = 2.94, xend = 3.06, y = median, yend = median, color = scenario), size = 0.5) +
  geom_segment(data = df_stat_30, aes(x = 1.94, xend = 2.06, y = median, yend = median, color = scenario), size = 0.5) +
    facet_wrap(~"Low or Zero Emitting Generation") +
    scale_y_continuous(limits = c(ymin, 6500), breaks = c(0, 3250 , 6500)) +
    scale_x_continuous(breaks = c(1,2,3), labels = c("2021", "2030", "2035")) +
    theme_emf() +
    scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.y = element_blank(), 
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks = element_blank(),
          legend.position = "none", 
          plot.margin = margin(0,0,0,0)) + 
  scale_alpha(range = c(0.6, 1), guide = F)

##### High Total #####
df_21 = high %>%
  filter(year %in% c(2021))
df_stat_21 = df_21 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_30 = high %>%
  filter(year %in% c(2030))
df_stat_30 = df_30 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))

df_35 = high %>%
  filter(year %in% c(2035))
df_stat_35 = df_35 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

mean_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","mean"]$mean - df_stat_30[df_stat_30$scenario == "IRA","mean"]$mean
mean_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","mean"]$mean - df_stat_35[df_stat_35$scenario == "IRA","mean"]$mean

median_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","median"]$median - df_stat_30[df_stat_30$scenario == "IRA","median"]$median
median_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","median"]$median - df_stat_35[df_stat_35$scenario == "IRA","median"]$median

stats = data.frame("year" = c(2030, 2035, 2030, 2035), "metric" = c("mean","mean","median","median"), 
                   "difference" = c(mean_diff_30, mean_diff_35,median_diff_30, median_diff_35))

data = rbind(df_21, df_30, df_35) 

 

data_High <- data %>%
  mutate(axe = case_when(
    year == 2021 ~ 1, 
    year == 2030 ~ 2, 
    year == 2035 ~ 3
  )) %>%
  mutate(scenario = case_when(
    year == 2021 ~ "Historic", 
    T ~ scenario)
  )

dots_High = ggplot(data = data_High, aes(x = axe, y = value,  color = scenario)) +
  geom_point(aes(alpha = alpha), shape = 1, size = 1.5, position = position_dodge(width = -0.5)) +
  geom_segment(data = df_stat_35, aes(x = 2.94, xend = 3.06, y = median, yend = median, color = scenario), size = 0.5) +
  geom_segment(data = df_stat_30, aes(x = 1.94, xend = 2.06, y = median, yend = median, color = scenario), size = 0.5) +
    facet_wrap(~"High Emitting Generation") +
    scale_y_continuous(limits = c(ymin, 6500), breaks = c(0, 3250 , 6500)) +
    scale_x_continuous(breaks = c(1,2,3), labels = c("2021", "2030", "2035")) +
    theme_emf() +
    scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.y = element_blank(), 
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks = element_blank(),
          legend.position = "none", 
          plot.margin = margin(0,0,0,0)) + 
  scale_alpha(range = c(0.6, 1), guide = F)

##### Nuclear #####
df_21 = individual[individual$variable_rename == "Nuclear", ] %>%
  filter(year %in% c(2021))
df_stat_21 = df_21 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_30 = individual[individual$variable_rename == "Nuclear", ] %>%
  filter(year %in% c(2030))
df_stat_30 = df_30 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_35 = individual[individual$variable_rename == "Nuclear", ] %>%
  filter(year %in% c(2035))
df_stat_35 = df_35 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

mean_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","mean"]$mean - df_stat_30[df_stat_30$scenario == "IRA","mean"]$mean
mean_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","mean"]$mean - df_stat_35[df_stat_35$scenario == "IRA","mean"]$mean

median_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","median"]$median - df_stat_30[df_stat_30$scenario == "IRA","median"]$median
median_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","median"]$median - df_stat_35[df_stat_35$scenario == "IRA","median"]$median

stats = data.frame("year" = c(2030, 2035, 2030, 2035), "metric" = c("mean","mean","median","median"), 
                   "difference" = c(mean_diff_30, mean_diff_35,median_diff_30, median_diff_35))

data = rbind(df_21, df_30, df_35) 

 

data_Nuclear <- data %>%
  mutate(axe = case_when(
    year == 2021 ~ 1, 
    year == 2030 ~ 2, 
    year == 2035 ~ 3
  )) %>%
  mutate(scenario = case_when(
    year == 2021 ~ "Historic", 
    T ~ scenario)
  )

dots_Nuclear = ggplot(data = data_Nuclear, aes(x = axe, y = value,  color = scenario)) +
  geom_point(aes(alpha = alpha), shape = 1, size = 1.5, position = position_dodge(width = -0.5)) +
  geom_segment(data = df_stat_35, aes(x = 2.94, xend = 3.06, y = median, yend = median, color = scenario), size = 0.5) +
  geom_segment(data = df_stat_30, aes(x = 1.94, xend = 2.06, y = median, yend = median, color = scenario), size = 0.5) +
    facet_wrap(~"Nuclear") +
    scale_y_continuous(limits = c(ymin, 2600), breaks = c(0, 1300 , 2600)) +
    scale_x_continuous(breaks = c(1,2,3), labels = c("2021", "2030", "2035")) +
    theme_emf() +
    scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.y = element_blank(), 
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks = element_blank(),
          legend.position = "none", 
          plot.margin = margin(0,0,0,0)) + 
  scale_alpha(range = c(0.6, 1), guide = F)

##### Solar #####
df_21 = individual[individual$variable_rename == "Solar", ] %>%
  filter(year %in% c(2021))
df_stat_21 = df_21 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_30 = individual[individual$variable_rename == "Solar", ] %>%
  filter(year %in% c(2030))
df_stat_30 = df_30 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_35 = individual[individual$variable_rename == "Solar", ] %>%
  filter(year %in% c(2035))
df_stat_35 = df_35 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

mean_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","mean"]$mean - df_stat_30[df_stat_30$scenario == "IRA","mean"]$mean
mean_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","mean"]$mean - df_stat_35[df_stat_35$scenario == "IRA","mean"]$mean

median_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","median"]$median - df_stat_30[df_stat_30$scenario == "IRA","median"]$median
median_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","median"]$median - df_stat_35[df_stat_35$scenario == "IRA","median"]$median

stats = data.frame("year" = c(2030, 2035, 2030, 2035), "metric" = c("mean","mean","median","median"), 
                   "difference" = c(mean_diff_30, mean_diff_35,median_diff_30, median_diff_35))

data = rbind(df_21, df_30, df_35) 

 

data_Solar <- data %>%
  mutate(axe = case_when(
    year == 2021 ~ 1, 
    year == 2030 ~ 2, 
    year == 2035 ~ 3
  )) %>%
  mutate(scenario = case_when(
    year == 2021 ~ "Historic", 
    T ~ scenario)
  )

dots_Solar = ggplot(data = data_Solar, aes(x = axe, y = value,  color = scenario)) +
  geom_point(aes(alpha = alpha), shape = 1, size = 1.5, position = position_dodge(width = -0.5)) +
  geom_segment(data = df_stat_35, aes(x = 2.94, xend = 3.06, y = median, yend = median, color = scenario), size = 0.5) +
  geom_segment(data = df_stat_30, aes(x = 1.94, xend = 2.06, y = median, yend = median, color = scenario), size = 0.5) +
    facet_wrap(~"Solar") +
    scale_y_continuous(limits = c(ymin, 2600), breaks = c(0, 1300 , 2600)) +
    scale_x_continuous(breaks = c(1,2,3), labels = c("2021", "2030", "2035")) +
    theme_emf() +
    scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.y = element_blank(), 
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks = element_blank(),
          legend.position = "none", 
          plot.margin = margin(0,0,0,0)) + 
  scale_alpha(range = c(0.6, 1), guide = F)

##### Wind #####

df_21 = individual[individual$variable_rename == "Wind", ] %>%
  filter(year %in% c(2021))
df_stat_21 = df_21 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_30 = individual[individual$variable_rename == "Wind", ] %>%
  filter(year %in% c(2030))
df_stat_30 = df_30 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_35 = individual[individual$variable_rename == "Wind", ] %>%
  filter(year %in% c(2035))
df_stat_35 = df_35 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

mean_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","mean"]$mean - df_stat_30[df_stat_30$scenario == "IRA","mean"]$mean
mean_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","mean"]$mean - df_stat_35[df_stat_35$scenario == "IRA","mean"]$mean

median_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","median"]$median - df_stat_30[df_stat_30$scenario == "IRA","median"]$median
median_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","median"]$median - df_stat_35[df_stat_35$scenario == "IRA","median"]$median

stats = data.frame("year" = c(2030, 2035, 2030, 2035), "metric" = c("mean","mean","median","median"), 
                   "difference" = c(mean_diff_30, mean_diff_35,median_diff_30, median_diff_35))

data = rbind(df_21, df_30, df_35) 

 

data_Wind <- data %>%
  mutate(axe = case_when(
    year == 2021 ~ 1, 
    year == 2030 ~ 2, 
    year == 2035 ~ 3
  )) %>%
  mutate(scenario = case_when(
    year == 2021 ~ "Historic", 
    T ~ scenario)
  )

dots_Wind = ggplot(data = data_Wind, aes(x = axe, y = value,  color = scenario)) +
  geom_point(aes(alpha = alpha), shape = 1, size = 1.5, position = position_dodge(width = -0.5)) +
  geom_segment(data = df_stat_35, aes(x = 2.94, xend = 3.06, y = median, yend = median, color = scenario), size = 0.5) +
  geom_segment(data = df_stat_30, aes(x = 1.94, xend = 2.06, y = median, yend = median, color = scenario), size = 0.5) +
    facet_wrap(~"Wind") +
    scale_y_continuous(limits = c(ymin, 2600), breaks = c(0, 1300 , 2600), labels = scales::comma) +
    scale_x_continuous(breaks = c(1,2,3), labels = c("2021", "2030", "2035")) +
    theme_emf() +
    labs(y = "TWh") +
    scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.x = element_blank(),
          axis.ticks = element_blank(),
          legend.position = "none", 
          plot.margin = margin(0,0,0,0)) + 
  scale_alpha(range = c(0.6, 1), guide = F)

##### CCS #####

df_21 = individual[individual$variable_rename == "CCS", ] %>%
  filter(year %in% c(2021))
df_stat_21 = df_21 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_30 = individual[individual$variable_rename == "CCS", ] %>%
  filter(year %in% c(2030))
df_stat_30 = df_30 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_35 = individual[individual$variable_rename == "CCS", ] %>%
  filter(year %in% c(2035))
df_stat_35 = df_35 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

mean_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","mean"]$mean - df_stat_30[df_stat_30$scenario == "IRA","mean"]$mean
mean_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","mean"]$mean - df_stat_35[df_stat_35$scenario == "IRA","mean"]$mean

median_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","median"]$median - df_stat_30[df_stat_30$scenario == "IRA","median"]$median
median_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","median"]$median - df_stat_35[df_stat_35$scenario == "IRA","median"]$median

stats = data.frame("year" = c(2030, 2035, 2030, 2035), "metric" = c("mean","mean","median","median"), 
                   "difference" = c(mean_diff_30, mean_diff_35,median_diff_30, median_diff_35))

data = rbind(df_21, df_30, df_35) 

 

data_CCS <- data %>%
  mutate(axe = case_when(
    year == 2021 ~ 1, 
    year == 2030 ~ 2, 
    year == 2035 ~ 3
  )) %>%
  mutate(scenario = case_when(
    year == 2021 ~ "Historic", 
    T ~ scenario)
  )

dots_CCS = ggplot(data = data_CCS, aes(x = axe, y = value,  color = scenario)) +
  geom_point(aes(alpha = alpha), shape = 1, size = 1.5, position = position_dodge(width = -0.5)) +
  geom_segment(data = df_stat_35, aes(x = 2.94, xend = 3.06, y = median, yend = median, color = scenario), size = 0.5) +
  geom_segment(data = df_stat_30, aes(x = 1.94, xend = 2.06, y = median, yend = median, color = scenario), size = 0.5) +
    facet_wrap(~"CCS") +
    scale_y_continuous(limits = c(ymin, 2600), breaks = c(0, 1300 , 2600)) +
    scale_x_continuous(breaks = c(1,2,3), labels = c("2021", "2030", "2035")) +
    theme_emf() +
    scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.y = element_blank(), 
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks = element_blank(),
          legend.position = "none", 
          plot.margin = margin(0,0,0,0)) + 
  scale_alpha(range = c(0.6, 1), guide = F)

##### Coal #####
df_21 = individual[individual$variable_rename == "Coal", ] %>%
  filter(year %in% c(2021))
df_stat_21 = df_21 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_30 = individual[individual$variable_rename == "Coal", ] %>%
  filter(year %in% c(2030))
df_stat_30 = df_30 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_35 = individual[individual$variable_rename == "Coal", ] %>%
  filter(year %in% c(2035))
df_stat_35 = df_35 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

mean_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","mean"]$mean - df_stat_30[df_stat_30$scenario == "IRA","mean"]$mean
mean_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","mean"]$mean - df_stat_35[df_stat_35$scenario == "IRA","mean"]$mean

median_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","median"]$median - df_stat_30[df_stat_30$scenario == "IRA","median"]$median
median_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","median"]$median - df_stat_35[df_stat_35$scenario == "IRA","median"]$median

stats = data.frame("year" = c(2030, 2035, 2030, 2035), "metric" = c("mean","mean","median","median"), 
                   "difference" = c(mean_diff_30, mean_diff_35,median_diff_30, median_diff_35))

data = rbind(df_21, df_30, df_35) 

 

data_Coal <- data %>%
  mutate(axe = case_when(
    year == 2021 ~ 1, 
    year == 2030 ~ 2, 
    year == 2035 ~ 3
  )) %>%
  mutate(scenario = case_when(
    year == 2021 ~ "Historic", 
    T ~ scenario)
  )

dots_Coal = ggplot(data = data_Coal, aes(x = axe, y = value,  color = scenario)) +
  geom_point(aes(alpha = alpha), shape = 1, size = 1.5, position = position_dodge(width = -0.5)) +
  geom_segment(data = df_stat_35, aes(x = 2.94, xend = 3.06, y = median, yend = median, color = scenario), size = 0.5) +
  geom_segment(data = df_stat_30, aes(x = 1.94, xend = 2.06, y = median, yend = median, color = scenario), size = 0.5) +
    facet_wrap(~"Coal") +
    scale_y_continuous(limits = c(ymin, 2600), breaks = c(0, 1300 , 2600), labels = scales::comma) +
    scale_x_continuous(breaks = c(1,2,3), labels = c("2021", "2030", "2035")) +
    theme_emf() +
    labs(y = "TWh") +
    scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.x = element_blank(),
          axis.ticks = element_blank(),
          legend.position = "none", 
          plot.margin = margin(0,0,0,0)) + 
  scale_alpha(range = c(0.6, 1), guide = F)

##### Gas #####
df_21 = individual[individual$variable_rename == "Natural Gas", ] %>%
  filter(year %in% c(2021))
df_stat_21 = df_21 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_30 = individual[individual$variable_rename == "Natural Gas", ] %>%
  filter(year %in% c(2030))
df_stat_30 = df_30 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_35 = individual[individual$variable_rename == "Natural Gas", ] %>%
  filter(year %in% c(2035))
df_stat_35 = df_35 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

mean_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","mean"]$mean - df_stat_30[df_stat_30$scenario == "IRA","mean"]$mean
mean_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","mean"]$mean - df_stat_35[df_stat_35$scenario == "IRA","mean"]$mean

median_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","median"]$median - df_stat_30[df_stat_30$scenario == "IRA","median"]$median
median_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","median"]$median - df_stat_35[df_stat_35$scenario == "IRA","median"]$median

stats = data.frame("year" = c(2030, 2035, 2030, 2035), "metric" = c("mean","mean","median","median"), 
                   "difference" = c(mean_diff_30, mean_diff_35,median_diff_30, median_diff_35))

data = rbind(df_21, df_30, df_35) 

 

data_Gas <- data %>%
  mutate(axe = case_when(
    year == 2021 ~ 1, 
    year == 2030 ~ 2, 
    year == 2035 ~ 3
  )) %>%
  mutate(scenario = case_when(
    year == 2021 ~ "Historic", 
    T ~ scenario)
  )

dots_Gas = ggplot(data = data_Gas, aes(x = axe, y = value,  color = scenario)) +
  geom_point(aes(alpha = alpha), shape = 1, size = 1.5, position = position_dodge(width = -0.5)) +
  geom_segment(data = df_stat_35, aes(x = 2.94, xend = 3.06, y = median, yend = median, color = scenario), size = 0.5) +
  geom_segment(data = df_stat_30, aes(x = 1.94, xend = 2.06, y = median, yend = median, color = scenario), size = 0.5) +
    facet_wrap(~"Natural Gas") +
    scale_y_continuous(limits = c(ymin, 2600), breaks = c(0, 1300 , 2600)) +
    scale_x_continuous(breaks = c(1,2,3), labels = c("2021", "2030", "2035")) +
    theme_emf() +
    scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.y = element_blank(), 
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks = element_blank(),
          legend.position = "none", 
          plot.margin = margin(0,0,0,0)) + 
  scale_alpha(range = c(0.6, 1), guide = F)

##### Other #####
df_21 = individual[individual$variable_rename == "Other", ] %>%
  filter(year %in% c(2021))
df_stat_21 = df_21 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_30 = individual[individual$variable_rename == "Other", ] %>%
  filter(year %in% c(2030))
df_stat_30 = df_30 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

df_35 = individual[individual$variable_rename == "Other", ] %>%
  filter(year %in% c(2035))
df_stat_35 = df_35 %>%
  group_by(scenario,year,variable_rename) %>%
  summarise(mean = mean(value),
            median = median(value))
  

mean_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","mean"]$mean - df_stat_30[df_stat_30$scenario == "IRA","mean"]$mean
mean_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","mean"]$mean - df_stat_35[df_stat_35$scenario == "IRA","mean"]$mean

median_diff_30 = df_stat_30[df_stat_30$scenario == "No IRA","median"]$median - df_stat_30[df_stat_30$scenario == "IRA","median"]$median
median_diff_35 = df_stat_35[df_stat_35$scenario == "No IRA","median"]$median - df_stat_35[df_stat_35$scenario == "IRA","median"]$median

stats = data.frame("year" = c(2030, 2035, 2030, 2035), "metric" = c("mean","mean","median","median"), 
                   "difference" = c(mean_diff_30, mean_diff_35,median_diff_30, median_diff_35))

data = rbind(df_21, df_30, df_35) 

 

data_Other <- data %>%
  mutate(axe = case_when(
    year == 2021 ~ 1, 
    year == 2030 ~ 2, 
    year == 2035 ~ 3
  )) %>%
  mutate(scenario = case_when(
    year == 2021 ~ "Historic", 
    T ~ scenario)
  )

dots_Other = ggplot(data = data_Other, aes(x = axe, y = value,  color = scenario)) +
  geom_point(aes(alpha = alpha), shape = 1, size = 1.5, position = position_dodge(width = -0.5)) +
  geom_segment(data = df_stat_35, aes(x = 2.94, xend = 3.06, y = median, yend = median, color = scenario), size = 0.5) +
  geom_segment(data = df_stat_30, aes(x = 1.94, xend = 2.06, y = median, yend = median, color = scenario), size = 0.5) +
    facet_wrap(~"Other") +
    scale_y_continuous(limits = c(ymin, 2600), breaks = c(0, 1300 , 2600)) +
    scale_x_continuous(breaks = c(1,2,3), labels = c("2021", "2030", "2035")) +
    theme_emf() +
    scale_subpalette(subpalettes, "Emissions|CO2|Energy|Demand|Industry") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.y = element_blank(), 
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks = element_blank(),
          legend.position = "none", 
          plot.margin = margin(0,0,0,0)) + 
  scale_alpha(range = c(0.6, 1), guide = F)

##### Final #####
final = (dots_Total | dots_Low | dots_High) / (dots_Wind | dots_Solar | dots_Nuclear | dots_CCS) / (dots_Coal | dots_Gas | dots_Other) 

final = final + 
  plot_layout(
  guides = "collect"
) & theme(legend.position = "bottom")
final

ggsave(filename = "output/final_figures/Fig2.4.svg", plot = final,width = 9, height = 8, units = "in")

ggsave(filename = "output/final_figures/Fig2.4.png", plot = final,width = 9, height = 8, units = "in")
```

### Table 2.4 Total

```{r}

title = "Total Electricity Generation"

fig = print_graph("time_series", config, clean_data, figmap_leep_timeseries, 16, "United States")

fig$data <- fig$data %>%
  filter(year == 2005 | year == 2021 | year == 2030 | year == 2035)%>%
  filter(!model == "EIA") %>%
  filter(!model == "EIA-STEO") %>%
  mutate(value = value/0.0036, 
         unit = "TWh")

total <- fig$data %>%
  group_by(scenario, model, year) %>%
  summarise(value = sum(value)) %>%
  mutate(variable_rename = "Total")

base <- total %>%
  filter(year == 2005 & model == "EIA-LTS")

baseline = base$value[1]

base <- as.data.frame(base) %>%
  select(Year = year, 
         `Absolute Level (TWh)` = value) %>%
  mutate(Scenario = "Baseline", 
    `% Reductions from 2005` = NA,
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA)  %>%
  select(Year, Scenario, `Absolute Level (TWh)`, `% Reductions from 2005`, `% Reductions from No IRA`, `Reductions from No IRA (TWh)`)

NoIRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "No IRA") %>%
  group_by(year) %>%
  summarize(`No IRA Median` = median(value), 
            `No IRA Min` = min(value),
            `No IRA Max` =  max(value))%>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(`2005_perc_red` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100) %>%
  mutate(
    Year = year, 
    `% Reductions from 2005` = `2005_perc_red`, 
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA
  ) %>%
  select(!year & !`2005_perc_red`)

IRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "IRA") %>%
  select(!scenario) %>%
  group_by(year) %>%
  summarize(
    `IRA Max` = max(value), 
    `IRA Min` = min(value), 
    `IRA Median` = median(value)) %>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(
    `% Reductions from 2005` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100
  )%>%
  mutate(
    `% Reductions from No IRA` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
      year == 2030 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
            year == 2035 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]) * 100
    ), 

    `Reductions from No IRA (TWh)` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
      year == 2030 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
            year == 2035 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)
    )
  ) %>%
  rename(Year = year)

IRA = rbind(NoIRA, IRA)


IRA <- IRA %>%
  arrange(desc(IRA)) %>%
  arrange(Year)

IRA = rbind(base, IRA)


IRA$`Absolute Level (TWh)` = round(IRA$`Absolute Level (TWh)`, 3)
IRA$`% Reductions from 2005` = round(IRA$`% Reductions from 2005`, 3)
IRA$`% Reductions from No IRA` = round(IRA$`% Reductions from No IRA`, 3)
IRA$`Reductions from No IRA (TWh)` = round(IRA$`Reductions from No IRA (TWh)`,3)

write.csv(IRA, paste0("./output/leep/", title, ".csv"), row.names = F)

IRA %>%
tableHTML(caption = paste(title), rownames = F)




```

### Table 2.4 Low

```{r}

title = "Low Emitting Electricity Generation"

fig = print_graph("time_series", config, clean_data, figmap_leep_timeseries, 16, "United States")

fig$data <- fig$data %>%
  filter(year == 2005 | year == 2021 | year == 2030 | year == 2035)%>%
  filter(!model == "EIA") %>%
  filter(!model == "EIA-STEO") %>%
  mutate(value = value/0.0036, 
         unit = "TWh")

total <- fig$data %>%
  filter(variable_rename == "CCS" | 
         variable_rename == "Other" |
         variable_rename == "Nuclear" |
         variable_rename == "Solar" |
         variable_rename == "Wind"
) %>%
  group_by(scenario, model, year) %>%
  summarise(value = sum(value)) %>%
  mutate(variable_rename = "Total_Low")

base <- total %>%
  filter(year == 2005 & model == "EIA-LTS")

baseline = base$value[1]

base <- as.data.frame(base) %>%
  select(Year = year, 
         `Absolute Level (TWh)` = value) %>%
  mutate(Scenario = "Baseline", 
    `% Reductions from 2005` = NA,
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA)  %>%
  select(Year, Scenario, `Absolute Level (TWh)`, `% Reductions from 2005`, `% Reductions from No IRA`, `Reductions from No IRA (TWh)`)

NoIRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "No IRA") %>%
  group_by(year) %>%
  summarize(`No IRA Median` = median(value), 
            `No IRA Min` = min(value),
            `No IRA Max` =  max(value))%>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(`2005_perc_red` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100) %>%
  mutate(
    Year = year, 
    `% Reductions from 2005` = `2005_perc_red`, 
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA
  ) %>%
  select(!year & !`2005_perc_red`)

IRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "IRA") %>%
  select(!scenario) %>%
  group_by(year) %>%
  summarize(
    `IRA Max` = max(value), 
    `IRA Min` = min(value), 
    `IRA Median` = median(value)) %>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(
    `% Reductions from 2005` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100
  )%>%
  mutate(
    `% Reductions from No IRA` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
      year == 2030 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
            year == 2035 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]) * 100
    ), 

    `Reductions from No IRA (TWh)` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
      year == 2030 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
            year == 2035 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)
    )
  ) %>%
  rename(Year = year)

IRA = rbind(NoIRA, IRA)



IRA <- IRA %>%
  arrange(desc(IRA)) %>%
  arrange(Year)

IRA = rbind(base, IRA)

IRA$`Absolute Level (TWh)` = round(IRA$`Absolute Level (TWh)`, 3)
IRA$`% Reductions from 2005` = round(IRA$`% Reductions from 2005`, 3)
IRA$`% Reductions from No IRA` = round(IRA$`% Reductions from No IRA`, 3)
IRA$`Reductions from No IRA (TWh)` = round(IRA$`Reductions from No IRA (TWh)`,3)

write.csv(IRA, paste0("./output/leep/", title, ".csv"), row.names = F)

IRA %>%
tableHTML(caption = paste(title), rownames = F)




```

### Table 2.4 High

```{r}

title = "High Emitting Electricity Generation"

fig = print_graph("time_series", config, clean_data, figmap_leep_timeseries, 16, "United States")

fig$data <- fig$data %>%
  filter(year == 2005 | year == 2021 | year == 2030 | year == 2035)%>%
  filter(!model == "EIA") %>%
  filter(!model == "EIA-STEO") %>%
  mutate(value = value/0.0036, 
         unit = "TWh")

total <- fig$data %>%
  filter(variable_rename == "Coal" |
         variable_rename == "Natural Gas" |
         variable_rename == "Oil"
) %>%
  group_by(scenario, model, year) %>%
  summarise(value = sum(value)) %>%
  mutate(variable_rename = "Total_High")

base <- total %>%
  filter(year == 2005 & model == "EIA-LTS")

baseline = base$value[1]

base <- as.data.frame(base) %>%
  select(Year = year, 
         `Absolute Level (TWh)` = value) %>%
  mutate(Scenario = "Baseline", 
    `% Reductions from 2005` = NA,
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA)  %>%
  select(Year, Scenario, `Absolute Level (TWh)`, `% Reductions from 2005`, `% Reductions from No IRA`, `Reductions from No IRA (TWh)`)

NoIRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "No IRA") %>%
  group_by(year) %>%
  summarize(`No IRA Median` = median(value), 
            `No IRA Min` = min(value),
            `No IRA Max` =  max(value))%>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(`2005_perc_red` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100) %>%
  mutate(
    Year = year, 
    `% Reductions from 2005` = `2005_perc_red`, 
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA
  ) %>%
  select(!year & !`2005_perc_red`)

IRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "IRA") %>%
  select(!scenario) %>%
  group_by(year) %>%
  summarize(
    `IRA Max` = max(value), 
    `IRA Min` = min(value), 
    `IRA Median` = median(value)) %>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(
    `% Reductions from 2005` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100
  )%>%
  mutate(
    `% Reductions from No IRA` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
      year == 2030 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
            year == 2035 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]) * 100
    ), 

    `Reductions from No IRA (TWh)` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
      year == 2030 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
            year == 2035 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)
    )
  ) %>%
  rename(Year = year)

IRA = rbind(NoIRA, IRA)



IRA <- IRA %>%
  arrange(desc(IRA)) %>%
  arrange(Year)

IRA = rbind(base, IRA)

IRA$`Absolute Level (TWh)` = round(IRA$`Absolute Level (TWh)`, 3)
IRA$`% Reductions from 2005` = round(IRA$`% Reductions from 2005`, 3)
IRA$`% Reductions from No IRA` = round(IRA$`% Reductions from No IRA`, 3)
IRA$`Reductions from No IRA (TWh)` = round(IRA$`Reductions from No IRA (TWh)`,3)

write.csv(IRA, paste0("./output/leep/", title, ".csv"), row.names = F)

IRA %>%
tableHTML(caption = paste(title), rownames = F)




```

### Table 2.4 Wind

```{r}

title = "Wind Electricity Generation"

fig = print_graph("time_series", config, clean_data, figmap_leep_timeseries, 16, "United States")

fig$data <- fig$data %>%
  filter(year == 2005 | year == 2021 | year == 2030 | year == 2035)%>%
  filter(!model == "EIA") %>%
  filter(!model == "EIA-STEO") %>%
  mutate(value = value/0.0036, 
         unit = "TWh")

total <- fig$data %>%
  mutate(
    variable_rename = case_when(variable_rename == "Oil" ~ "Other", 
                                T ~ variable_rename)
  ) %>%
  group_by(year, variable_rename, model, scenario) %>%
  summarise(value = sum(value)) %>%
  filter(variable_rename == "Wind")

base <- total %>%
  filter(year == 2005 & model == "EIA-LTS")

baseline = base$value[1]

base <- as.data.frame(base) %>%
  select(Year = year, 
         `Absolute Level (TWh)` = value) %>%
  mutate(Scenario = "Baseline", 
    `% Reductions from 2005` = NA,
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA)  %>%
  select(Year, Scenario, `Absolute Level (TWh)`, `% Reductions from 2005`, `% Reductions from No IRA`, `Reductions from No IRA (TWh)`)

NoIRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "No IRA") %>%
  group_by(year) %>%
  summarize(`No IRA Median` = median(value), 
            `No IRA Min` = min(value),
            `No IRA Max` =  max(value))%>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(`2005_perc_red` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100) %>%
  mutate(
    Year = year, 
    `% Reductions from 2005` = `2005_perc_red`, 
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA
  ) %>%
  select(!year & !`2005_perc_red`)

IRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "IRA") %>%
  select(!scenario) %>%
  group_by(year) %>%
  summarize(
    `IRA Max` = max(value), 
    `IRA Min` = min(value), 
    `IRA Median` = median(value)) %>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(
    `% Reductions from 2005` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100
  )%>%
  mutate(
    `% Reductions from No IRA` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
      year == 2030 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
            year == 2035 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]) * 100
    ), 

    `Reductions from No IRA (TWh)` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
      year == 2030 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
            year == 2035 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)
    )
  ) %>%
  rename(Year = year)

IRA = rbind(NoIRA, IRA)



IRA <- IRA %>%
  arrange(desc(IRA)) %>%
  arrange(Year)

IRA = rbind(base, IRA)

IRA$`Absolute Level (TWh)` = round(IRA$`Absolute Level (TWh)`, 3)
IRA$`% Reductions from 2005` = round(IRA$`% Reductions from 2005`, 3)
IRA$`% Reductions from No IRA` = round(IRA$`% Reductions from No IRA`, 3)
IRA$`Reductions from No IRA (TWh)` = round(IRA$`Reductions from No IRA (TWh)`,3)

write.csv(IRA, paste0("./output/leep/", title, ".csv"), row.names = F)

IRA %>%
tableHTML(caption = paste(title), rownames = F)




```

### Table 2.4 Solar

```{r}

title = "Solar Electricity Generation"

fig = print_graph("time_series", config, clean_data, figmap_leep_timeseries, 16, "United States")

fig$data <- fig$data %>%
  filter(year == 2005 | year == 2021 | year == 2030 | year == 2035)%>%
  filter(!model == "EIA") %>%
  filter(!model == "EIA-STEO") %>%
  mutate(value = value/0.0036, 
         unit = "TWh")

total <- fig$data %>%
  mutate(
    variable_rename = case_when(variable_rename == "Oil" ~ "Other", 
                                T ~ variable_rename)
  ) %>%
  group_by(year, variable_rename, model, scenario) %>%
  summarise(value = sum(value)) %>%
  filter(variable_rename == "Solar")

base <- total %>%
  filter(year == 2005 & model == "EIA-LTS")

baseline = base$value[1]

base <- as.data.frame(base) %>%
  select(Year = year, 
         `Absolute Level (TWh)` = value) %>%
  mutate(Scenario = "Baseline", 
    `% Reductions from 2005` = NA,
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA)  %>%
  select(Year, Scenario, `Absolute Level (TWh)`, `% Reductions from 2005`, `% Reductions from No IRA`, `Reductions from No IRA (TWh)`)

NoIRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "No IRA") %>%
  group_by(year) %>%
  summarize(`No IRA Median` = median(value), 
            `No IRA Min` = min(value),
            `No IRA Max` =  max(value))%>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(`2005_perc_red` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100) %>%
  mutate(
    Year = year, 
    `% Reductions from 2005` = `2005_perc_red`, 
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA
  ) %>%
  select(!year & !`2005_perc_red`)

IRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "IRA") %>%
  select(!scenario) %>%
  group_by(year) %>%
  summarize(
    `IRA Max` = max(value), 
    `IRA Min` = min(value), 
    `IRA Median` = median(value)) %>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(
    `% Reductions from 2005` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100
  )%>%
  mutate(
    `% Reductions from No IRA` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
      year == 2030 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
            year == 2035 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]) * 100
    ), 

    `Reductions from No IRA (TWh)` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
      year == 2030 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
            year == 2035 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)
    )
  ) %>%
  rename(Year = year)

IRA = rbind(NoIRA, IRA)



IRA <- IRA %>%
  arrange(desc(IRA)) %>%
  arrange(Year)

IRA = rbind(base, IRA)

IRA$`Absolute Level (TWh)` = round(IRA$`Absolute Level (TWh)`, 3)
IRA$`% Reductions from 2005` = round(IRA$`% Reductions from 2005`, 3)
IRA$`% Reductions from No IRA` = round(IRA$`% Reductions from No IRA`, 3)
IRA$`Reductions from No IRA (TWh)` = round(IRA$`Reductions from No IRA (TWh)`,3)

write.csv(IRA, paste0("./output/leep/", title, ".csv"), row.names = F)

IRA %>%
tableHTML(caption = paste(title), rownames = F)




```

### Table 2.4 Nuclear

```{r}

title = "Nuclear Electricity Generation"

fig = print_graph("time_series", config, clean_data, figmap_leep_timeseries, 16, "United States")

fig$data <- fig$data %>%
  filter(year == 2005 | year == 2021 | year == 2030 | year == 2035)%>%
  filter(!model == "EIA") %>%
  filter(!model == "EIA-STEO") %>%
  mutate(value = value/0.0036, 
         unit = "TWh")

total <- fig$data %>%
  mutate(
    variable_rename = case_when(variable_rename == "Oil" ~ "Other", 
                                T ~ variable_rename)
  ) %>%
  group_by(year, variable_rename, model, scenario) %>%
  summarise(value = sum(value)) %>%
  filter(variable_rename == "Nuclear")

base <- total %>%
  filter(year == 2005 & model == "EIA-LTS")

baseline = base$value[1]

base <- as.data.frame(base) %>%
  select(Year = year, 
         `Absolute Level (TWh)` = value) %>%
  mutate(Scenario = "Baseline", 
    `% Reductions from 2005` = NA,
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA)  %>%
  select(Year, Scenario, `Absolute Level (TWh)`, `% Reductions from 2005`, `% Reductions from No IRA`, `Reductions from No IRA (TWh)`)

NoIRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "No IRA") %>%
  group_by(year) %>%
  summarize(`No IRA Median` = median(value), 
            `No IRA Min` = min(value),
            `No IRA Max` =  max(value))%>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(`2005_perc_red` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100) %>%
  mutate(
    Year = year, 
    `% Reductions from 2005` = `2005_perc_red`, 
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA
  ) %>%
  select(!year & !`2005_perc_red`)

IRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "IRA") %>%
  select(!scenario) %>%
  group_by(year) %>%
  summarize(
    `IRA Max` = max(value), 
    `IRA Min` = min(value), 
    `IRA Median` = median(value)) %>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(
    `% Reductions from 2005` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100
  )%>%
  mutate(
    `% Reductions from No IRA` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
      year == 2030 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
            year == 2035 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]) * 100
    ), 

    `Reductions from No IRA (TWh)` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
      year == 2030 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
            year == 2035 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)
    )
  ) %>%
  rename(Year = year)

IRA = rbind(NoIRA, IRA)



IRA <- IRA %>%
  arrange(desc(IRA)) %>%
  arrange(Year)

IRA = rbind(base, IRA)

IRA$`Absolute Level (TWh)` = round(IRA$`Absolute Level (TWh)`, 3)
IRA$`% Reductions from 2005` = round(IRA$`% Reductions from 2005`, 3)
IRA$`% Reductions from No IRA` = round(IRA$`% Reductions from No IRA`, 3)
IRA$`Reductions from No IRA (TWh)` = round(IRA$`Reductions from No IRA (TWh)`,3)

write.csv(IRA, paste0("./output/leep/", title, ".csv"), row.names = F)

IRA %>%
tableHTML(caption = paste(title), rownames = F)




```

### Table 2.4 CCS

```{r}

title = "CCS Electricity Generation"

fig = print_graph("time_series", config, clean_data, figmap_leep_timeseries, 16, "United States")

fig$data <- fig$data %>%
  filter(year == 2005 | year == 2021 | year == 2030 | year == 2035)%>%
  filter(!model == "EIA") %>%
  filter(!model == "EIA-STEO") %>%
  mutate(value = value/0.0036, 
         unit = "TWh")

total <- fig$data %>%
  mutate(
    variable_rename = case_when(variable_rename == "Oil" ~ "Other", 
                                T ~ variable_rename)
  ) %>%
  group_by(year, variable_rename, model, scenario) %>%
  summarise(value = sum(value)) %>%
  filter(variable_rename == "CCS")

base <- total %>%
  filter(year == 2005 & model == "EIA-LTS")

baseline = base$value[1]

base <- as.data.frame(base) %>%
  select(Year = year, 
         `Absolute Level (TWh)` = value) %>%
  mutate(Scenario = "Baseline", 
    `% Reductions from 2005` = NA,
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA)  %>%
  select(Year, Scenario, `Absolute Level (TWh)`, `% Reductions from 2005`, `% Reductions from No IRA`, `Reductions from No IRA (TWh)`)

NoIRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "No IRA") %>%
  group_by(year) %>%
  summarize(`No IRA Median` = median(value), 
            `No IRA Min` = min(value),
            `No IRA Max` =  max(value))%>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(`2005_perc_red` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100) %>%
  mutate(
    Year = year, 
    `% Reductions from 2005` = `2005_perc_red`, 
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA
  ) %>%
  select(!year & !`2005_perc_red`)

IRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "IRA") %>%
  select(!scenario) %>%
  group_by(year) %>%
  summarize(
    `IRA Max` = max(value), 
    `IRA Min` = min(value), 
    `IRA Median` = median(value)) %>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(
    `% Reductions from 2005` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100
  )%>%
  mutate(
    `% Reductions from No IRA` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
      year == 2030 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
            year == 2035 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]) * 100
    ), 

    `Reductions from No IRA (TWh)` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
      year == 2030 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
            year == 2035 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)
    )
  ) %>%
  rename(Year = year)

IRA = rbind(NoIRA, IRA)



IRA <- IRA %>%
  arrange(desc(IRA)) %>%
  arrange(Year)

IRA = rbind(base, IRA)

IRA$`Absolute Level (TWh)` = round(IRA$`Absolute Level (TWh)`, 3)
IRA$`% Reductions from 2005` = round(IRA$`% Reductions from 2005`, 3)
IRA$`% Reductions from No IRA` = round(IRA$`% Reductions from No IRA`, 3)
IRA$`Reductions from No IRA (TWh)` = round(IRA$`Reductions from No IRA (TWh)`,3)

write.csv(IRA, paste0("./output/leep/", title, ".csv"), row.names = F)

IRA %>%
tableHTML(caption = paste(title), rownames = F)




```

### Table 2.4 Coal

```{r}

title = "Coal Electricity Generation"

fig = print_graph("time_series", config, clean_data, figmap_leep_timeseries, 16, "United States")

fig$data <- fig$data %>%
  filter(year == 2005 | year == 2021 | year == 2030 | year == 2035)%>%
  filter(!model == "EIA") %>%
  filter(!model == "EIA-STEO") %>%
  mutate(value = value/0.0036, 
         unit = "TWh")

total <- fig$data %>%
  mutate(
    variable_rename = case_when(variable_rename == "Oil" ~ "Other", 
                                T ~ variable_rename)
  ) %>%
  group_by(year, variable_rename, model, scenario) %>%
  summarise(value = sum(value)) %>%
  filter(variable_rename == "Coal")

base <- total %>%
  filter(year == 2005 & model == "EIA-LTS")

baseline = base$value[1]

base <- as.data.frame(base) %>%
  select(Year = year, 
         `Absolute Level (TWh)` = value) %>%
  mutate(Scenario = "Baseline", 
    `% Reductions from 2005` = NA,
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA)  %>%
  select(Year, Scenario, `Absolute Level (TWh)`, `% Reductions from 2005`, `% Reductions from No IRA`, `Reductions from No IRA (TWh)`)

NoIRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "No IRA") %>%
  group_by(year) %>%
  summarize(`No IRA Median` = median(value), 
            `No IRA Min` = min(value),
            `No IRA Max` =  max(value))%>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(`2005_perc_red` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100) %>%
  mutate(
    Year = year, 
    `% Reductions from 2005` = `2005_perc_red`, 
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA
  ) %>%
  select(!year & !`2005_perc_red`)

IRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "IRA") %>%
  select(!scenario) %>%
  group_by(year) %>%
  summarize(
    `IRA Max` = max(value), 
    `IRA Min` = min(value), 
    `IRA Median` = median(value)) %>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(
    `% Reductions from 2005` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100
  )%>%
  mutate(
    `% Reductions from No IRA` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
      year == 2030 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
            year == 2035 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]) * 100
    ), 

    `Reductions from No IRA (TWh)` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
      year == 2030 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
            year == 2035 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)
    )
  ) %>%
  rename(Year = year)

IRA = rbind(NoIRA, IRA)



IRA <- IRA %>%
  arrange(desc(IRA)) %>%
  arrange(Year)

IRA = rbind(base, IRA)

IRA$`Absolute Level (TWh)` = round(IRA$`Absolute Level (TWh)`, 3)
IRA$`% Reductions from 2005` = round(IRA$`% Reductions from 2005`, 3)
IRA$`% Reductions from No IRA` = round(IRA$`% Reductions from No IRA`, 3)
IRA$`Reductions from No IRA (TWh)` = round(IRA$`Reductions from No IRA (TWh)`,3)

write.csv(IRA, paste0("./output/leep/", title, ".csv"), row.names = F)

IRA %>%
tableHTML(caption = paste(title), rownames = F)




```

### Table 2.4 Gas

```{r}

title = "Nautural Gas Electricity Generation"

fig = print_graph("time_series", config, clean_data, figmap_leep_timeseries, 16, "United States")

fig$data <- fig$data %>%
  filter(year == 2005 | year == 2021 | year == 2030 | year == 2035)%>%
  filter(!model == "EIA") %>%
  filter(!model == "EIA-STEO") %>%
  mutate(value = value/0.0036, 
         unit = "TWh")

total <- fig$data %>%
  mutate(
    variable_rename = case_when(variable_rename == "Oil" ~ "Other", 
                                T ~ variable_rename)
  ) %>%
  group_by(year, variable_rename, model, scenario) %>%
  summarise(value = sum(value)) %>%
  filter(variable_rename == "Natural Gas")

base <- total %>%
  filter(year == 2005 & model == "EIA-LTS")

baseline = base$value[1]

base <- as.data.frame(base) %>%
  select(Year = year, 
         `Absolute Level (TWh)` = value) %>%
  mutate(Scenario = "Baseline", 
    `% Reductions from 2005` = NA,
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA)  %>%
  select(Year, Scenario, `Absolute Level (TWh)`, `% Reductions from 2005`, `% Reductions from No IRA`, `Reductions from No IRA (TWh)`)

NoIRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "No IRA") %>%
  group_by(year) %>%
  summarize(`No IRA Median` = median(value), 
            `No IRA Min` = min(value),
            `No IRA Max` =  max(value))%>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(`2005_perc_red` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100) %>%
  mutate(
    Year = year, 
    `% Reductions from 2005` = `2005_perc_red`, 
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA
  ) %>%
  select(!year & !`2005_perc_red`)

IRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "IRA") %>%
  select(!scenario) %>%
  group_by(year) %>%
  summarize(
    `IRA Max` = max(value), 
    `IRA Min` = min(value), 
    `IRA Median` = median(value)) %>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(
    `% Reductions from 2005` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100
  )%>%
  mutate(
    `% Reductions from No IRA` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
      year == 2030 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
            year == 2035 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]) * 100
    ), 

    `Reductions from No IRA (TWh)` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
      year == 2030 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
            year == 2035 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)
    )
  ) %>%
  rename(Year = year)

IRA = rbind(NoIRA, IRA)



IRA <- IRA %>%
  arrange(desc(IRA)) %>%
  arrange(Year)

IRA = rbind(base, IRA)

IRA$`Absolute Level (TWh)` = round(IRA$`Absolute Level (TWh)`, 3)
IRA$`% Reductions from 2005` = round(IRA$`% Reductions from 2005`, 3)
IRA$`% Reductions from No IRA` = round(IRA$`% Reductions from No IRA`, 3)
IRA$`Reductions from No IRA (TWh)` = round(IRA$`Reductions from No IRA (TWh)`,3)

write.csv(IRA, paste0("./output/leep/", title, ".csv"), row.names = F)

IRA %>%
tableHTML(caption = paste(title), rownames = F)




```

### Table 2.4 Other

```{r}

title = "Other Electricity Generation"

fig = print_graph("time_series", config, clean_data, figmap_leep_timeseries, 16, "United States")

fig$data <- fig$data %>%
  filter(year == 2005 | year == 2021 | year == 2030 | year == 2035)%>%
  filter(!model == "EIA") %>%
  filter(!model == "EIA-STEO") %>%
  mutate(value = value/0.0036, 
         unit = "TWh")

total <- fig$data %>%
  mutate(
    variable_rename = case_when(variable_rename == "Oil" ~ "Other", 
                                T ~ variable_rename)
  ) %>%
  group_by(year, variable_rename, model, scenario) %>%
  summarise(value = sum(value)) %>%
  filter(variable_rename == "Other")

base <- total %>%
  filter(year == 2005 & model == "EIA-LTS")

baseline = base$value[1]

base <- as.data.frame(base) %>%
  select(Year = year, 
         `Absolute Level (TWh)` = value) %>%
  mutate(Scenario = "Baseline", 
    `% Reductions from 2005` = NA,
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA)  %>%
  select(Year, Scenario, `Absolute Level (TWh)`, `% Reductions from 2005`, `% Reductions from No IRA`, `Reductions from No IRA (TWh)`)

NoIRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "No IRA") %>%
  group_by(year) %>%
  summarize(`No IRA Median` = median(value), 
            `No IRA Min` = min(value),
            `No IRA Max` =  max(value))%>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(`2005_perc_red` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100) %>%
  mutate(
    Year = year, 
    `% Reductions from 2005` = `2005_perc_red`, 
    `% Reductions from No IRA` = NA, 
    `Reductions from No IRA (TWh)` = NA
  ) %>%
  select(!year & !`2005_perc_red`)

IRA <- total %>%
  filter(year == 2021 | year == 2030 | year == 2035) %>%
  filter(scenario == "IRA") %>%
  select(!scenario) %>%
  group_by(year) %>%
  summarize(
    `IRA Max` = max(value), 
    `IRA Min` = min(value), 
    `IRA Median` = median(value)) %>%
  pivot_longer(cols = !year, names_to = "Scenario", values_to = "Absolute Level (TWh)") %>%
  mutate(
    `% Reductions from 2005` = ((baseline-`Absolute Level (TWh)`)/baseline) * 100
  )%>%
  mutate(
    `% Reductions from No IRA` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
      year == 2030 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]) * 100,
      
            year == 2035 & Scenario == "IRA Max" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]) * 100, 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]) * 100, 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        ((NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)/NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]) * 100
    ), 

    `Reductions from No IRA (TWh)` = case_when(
            year == 2021 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2021 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2021 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
      year == 2030 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2030 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2030 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`),
      
            year == 2035 & Scenario == "IRA Max" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Max"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Median" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Median"]-`Absolute Level (TWh)`), 
      
      year == 2035 & Scenario == "IRA Min" ~ 
        (NoIRA$`Absolute Level (TWh)`[NoIRA$Year == 2035 & NoIRA$Scenario == "No IRA Min"]-`Absolute Level (TWh)`)
    )
  ) %>%
  rename(Year = year)

IRA = rbind(NoIRA, IRA)



IRA <- IRA %>%
  arrange(desc(IRA)) %>%
  arrange(Year)

IRA = rbind(base, IRA)

IRA$`Absolute Level (TWh)` = round(IRA$`Absolute Level (TWh)`, 3)
IRA$`% Reductions from 2005` = round(IRA$`% Reductions from 2005`, 3)
IRA$`% Reductions from No IRA` = round(IRA$`% Reductions from No IRA`, 3)
IRA$`Reductions from No IRA (TWh)` = round(IRA$`Reductions from No IRA (TWh)`,3)

write.csv(IRA, paste0("./output/leep/", title, ".csv"), row.names = F)

IRA %>%
tableHTML(caption = paste(title), rownames = F)
```

## 2.5 historical and projected capacity additions by technology

```{r}
# capacity addition plot

ymin = -40
ymax = 130

subpalettes = create_subpalettes(figmap_leep_stackbar, config)

fig = print_graph("stacked_bar", config, clean_data, figmap_leep_stackbar, 4, "United States") +
  geom_hline(yintercept = 0, linewidth = 0.25, color = "black") +
  scale_subpalette(subpalettes, "Capacity Additions2") +
  scale_y_continuous(limits = c(ymin, ymax)) +
  ggtitle("Historical Annual Capacity Changes") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10),
        axis.text.x = element_text(angle = 45))

dta = data_from_graph("stacked_bar", config, clean_data, figmap_leep_stackbar, 4, "United States")

#fig

dta4 = data_from_graph("stacked_bar", config, clean_data, figmap_leep_stackbar, 6, "United States")
dta_ttl = dta4 %>% 
  mutate(temp = case_when(
    grepl("Additions",variable) ~ "Capacity Additions",
    TRUE ~ "Capacity Retirements")) %>%
  group_by(model, scenario, region, datasrc, unit, temp) %>%
  summarize(value = sum(value)) %>% 
  select(-temp) %>%
  mutate(variable_rename = "Total")

dta4 = rbind(dta4,dta_ttl) %>% mutate(variable_rename = factor(variable_rename, 
                                  levels = c("Total", "Solar", "Wind", "Storage", "Nuclear", "Hydro", "Gas CCS", "Gas", "Coal CCS", "Coal"))) %>%
  mutate(stagger = case_when((variable_rename %in% c("Coal", "Nuclear", "Gas", "Total") & (value >= 0)) ~ -0.1,
                             (variable_rename %in% c("Coal", "Nuclear", "Gas", "Total") & (value < 0)) ~ 0.1,
                             TRUE ~ 0))

stats = dta4 %>% group_by(variable_rename, stagger) %>% summarize(mean = mean(value), median = median(value))

dotplot2 = dta4 %>% ggplot() + 
  geom_point(aes(x = (as.numeric(variable_rename) + stagger), y = value, color = variable_rename), shape = 16, size = 2) + 
  #geom_point(data = stats, aes(x = variable_rename, y = median, color = variable_rename), shape = 3, size = 2) +
  geom_segment(data = stats, aes(x = as.numeric(variable_rename) - 0.25 + stagger, xend = as.numeric(variable_rename) + 0.25 + stagger, 
                                 y = median, yend = median, color = variable_rename), linewidth = 0.5) +
  geom_hline(yintercept = 0, linewidth = 0.25, color = "black") +
  scale_x_continuous(breaks = seq(1,10), labels = c("Total", "Solar", "Wind", "Storage", "Nuclear", "Hydro", "Gas CCS", "Gas", "Coal CCS", "Coal")) +
  scale_y_continuous(limits = c(ymin, ymax)) +
  scale_subpalette(subpalettes, "Capacity Additions2") +
  ggtitle("Average Annual Capacity Changes (2021-2035)") +
  theme_emf() +
  theme(plot.title = element_text(hjust = 0.5, size = 10), axis.text.y = element_blank(),
        axis.title.y = element_blank(), axis.ticks = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")
#dotplot2
  

combined = 
  fig + dotplot2 + 
  plot_annotation(theme = theme(plot.title = element_text(hjust = 0.5))) +
    plot_layout(widths = c(1,1)) +
    theme(plot.margin = margin(0,0,0,0))
    # bottom1
combined


ggsave(filename = "output/final_figures/svg/Fig2.4_capacity.svg",combined, width = 7, height = 5, units = "in")
ggsave(filename = "output/final_figures/png/Fig2.4_capacity.png",combined, width = 7, height = 5, units = "in")
print(stats)

#suporting data for plot
dta = data_from_graph("stacked_bar", config, clean_data, figmap_leep_stackbar, 4, "United States")
dta %>% write.csv("output/final_figures/data/Fig2.4_capacity_bars.csv", row.names = FALSE)
dta4 %>% write.csv("output/final_figures/data/Fig2.4_capacity_dots.csv", row.names = FALSE)

```

## 2.6 sensitivity of electric sector emissions

```{r}
# electric sector emissions sensitivity dot plots
panel1_scens = c("Core","IRA", "IRA.Low","IRA.High")
panel2_scens = c("Low Growth", "High Growth", "Core") # Economic Growth
panel3_scens = c("Low Gas Price","High Gas Price", "Core") # Energy Prices
panel4_scens = c("All Advanced", "Adv Battery/Renew", "Cons Battery/Renew", "Core") # Technology Cost
panel5_scens = c("Constrained Deployment", "Core") # Deployment Constraints

sens_dta = clean_data %>% filter(variable == "Emissions|CO2|Energy|Supply|Electricity",
                                 year %in% c(2030, 2035)) #%>% 
#  mutate(year = factor(year))

print(max(sens_dta$value))
print(min(sens_dta$value))

filler = data.frame(year = c(203), value = c(-200), scenario = c(""), model = c("NA"))

sens_dta_panel1 = sens_dta %>% filter(scenario %in% panel1_scens) %>%
  filter(model %in% c("EPS-EI", "GCAM-CGS","RIO-REPEAT","REGEN-EPRI")) %>%
  mutate(stagger = case_when(
    scenario == "IRA.Low" ~ -0.7,
    scenario == "IRA.High" ~ 0.7,
    TRUE ~ 0
  ))
sens_dta_panel2 = sens_dta %>% filter(scenario %in% panel2_scens) %>% #mutate(value = -200) %>%
  bind_rows(filler)
sens_dta_panel3 = sens_dta %>% filter(scenario %in% panel3_scens) %>%
  bind_rows(filler)
sens_dta_panel4 = sens_dta %>% filter(scenario %in% panel4_scens) %>% 
  bind_rows(filler)
sens_dta_panel5 = sens_dta %>% filter(scenario %in% panel5_scens) %>%
  bind_rows(filler)

p1 = sens_dot_plot(sens_dta_panel1, title = "IRA Implementation", ymin = 0, ymax = 1600, far_left = TRUE, 
                   ira_coord = c(2030,1020), low_coord = c(2028.7, 1200), high_coord = c(2030, 620))
# p1
p2 = sens_dot_plot(sens_dta_panel2, title = "Economic Growth", ymin = 0, ymax = 1600,)
#p2
p3 = sens_dot_plot(sens_dta_panel3, title = "Natural Gas Price", ymin = 0, ymax = 1600,)
# p3
p4 = sens_dot_plot(sens_dta_panel4, title = "Technology Cost", ymin = 0, ymax = 1600,)
# p4
p5 = sens_dot_plot(sens_dta_panel5, title = "Constrained Deployment", ymin = 0, ymax = 1600,)
# p5

combined = (p1$plot | p2$plot | p3$plot | p4$plot | p5$plot) +
  plot_annotation(title = "Electric Sector CO2 Emissions", 
                  theme = theme(plot.title = element_blank()))
  
combined

ggsave(filename = "output/final_figures/svg/Fig2.5_elec_sensitivity_dots.svg",combined, width = 7, height = 5, units = "in")
ggsave(filename = "output/final_figures/png/Fig2.5_elec_sensitivity_dots.png",combined, width = 7, height = 5, units = "in")

# supporting data for figure
dta = bind_rows(sens_dta_panel1, sens_dta_panel3, sens_dta_panel4, sens_dta_panel5)
dta %>% write.csv("output/final_figures/data/Fig2.5_elec_sensitivity_dots.csv", row.names = FALSE)


#View(sens_dta)
```

## 2.7 & 2.8 nox and so2 emissions

```{r}
clean_data7 = clean_data %>% duplicate_historical_data("EPA",2021, criteria = TRUE) %>%
  mutate(alpha = case_when(
    model == "USREP-ReEDS" ~ 1,
    model == "GCAM-PNNL" ~ 1,
    model == "IPM-EPA" ~ 1,
    scenario == "Historic" ~ 1,
    TRUE ~ 0.8)
  ) %>%
  filter(value > 1e-4)

nox = print_graph("time_series", config, clean_data7, figmap_leep_timeseries, 122, "United States") +
  scale_alpha(range = c(0.6, 1), guide = "none")
#nox

sox = print_graph("time_series", config, clean_data7, figmap_leep_timeseries, 123, "United States") +
  scale_alpha(range = c(0.6, 1), guide = "none")
#sox

nox_full = dot_plots("time_series", config, clean_data7, figmap_leep_timeseries, 122, "United States", 0, 3, "Power Sector NOx Emissions", metric = "median", 
                     historic_coord = c(2015,1.8), preira_coord = c(2030, 0.95), ira_coord = c(2029, 0.15))
print(nox_full$full)
print(nox_full$stats)
ggsave(filename = "output/final_figures/svg/Fig2.7_nox.svg",nox_full$full, width = 7, height = 5, units = "in")
ggsave(filename = "output/final_figures/png/Fig2.7_nox.png",nox_full$full, width = 7, height = 5, units = "in")

sox_full = dot_plots("time_series", config, clean_data7, figmap_leep_timeseries, 123, "United States", 0, 5, "Power Sector SO2 Emissions", metric = "median", 
                     historic_coord = c(2017,2), preira_coord = c(2030, 1.2), ira_coord = c(2029, 0.12))
print(sox_full$full)
print(sox_full$stats)
ggsave(filename = "output/final_figures/svg/Fig2.8_sox.svg",sox_full$full, width = 7, height = 5, units = "in")
ggsave(filename = "output/final_figures/png/Fig2.8_sox.png",sox_full$full, width = 7, height = 5, units = "in")



dta1 = data_from_graph("time_series", config, clean_data7, figmap_leep_timeseries, 122, "United States")
dta2 = data_from_graph("time_series", config, clean_data7, figmap_leep_timeseries, 123, "United States")
dta1 %>% write.csv("output/final_figures/data/Fig2.7_nox.csv", row.names = FALSE)
dta2 %>% write.csv("output/final_figures/data/Fig2.8_sox.csv", row.names = FALSE)

# View(dta)
```









